Can Cultural Transmission Explain The Evolution of Cooperative Behaviour

### 2020-03-04 ms/main.tex
remove proposal stuff
revise intro

\title{Research Proposal:\\  Can Cultural Transmission Explain The Evolution of Cooperative Behavior}
\author{Dor Cohen \\ cohensdor@gmail.com \and Yoav Ram \\ yoav@yoavram.com}
\date{School of Computer Science, IDC Herzliya\\ \today}

@@

\section*{Introduction}
Cooperative behavior is interesting in evolutionary view. The theory of evolution is based on the the struggle of the individual to survive and reproduce. Natural selection favours those with the highest fitness and therefore, their reproduction will be the most successful. However, cooperative behavior can many times harm the individual's fitness and increase the fitness of its competitor \cite{axelrod1981evolution}. Yet cooperative behavior is a widespread phenomenon and occurs in other animals besides humans \cite{dugatkin1997cooperation}, for example in rats \cite{rice1962altruism} and birds \cite{krams2008experimental}.
Therefore, the evolution of cooperative behavior is still an interesting important open question.
\\Cultural evolution is an evolutionary theory of social change. Culture has significant impact on the behavior of animals \cite{bonner2018evolution} and humans \cite{ihara2004cultural,jeong2018bronze}. Individual can acquire new behavior from another individual in its social group  through learning or other modes of cultural transmission \cite{richerson2008not}.
\textbf{The goal of this research} is to determine to what extent cultural transmission can explain the evolution of cooperative behavior.
\subsection*{Theories for Evolution of Cooperation}
Three major theories have been proposed to explain the evolution of cooperative behavior.
\\\textbf{Kin selection}, proposing that natural selection can favour cooperative behaviour between kin. The importance of relatedness to the evolution of cooperation and altruism was shown by Hamilton \cite{hamilton1964genetical}. According to Hamilton, kin selection causes allele to increase in frequency when the genetic relatedness $r$ of a recipient to an actor multiplied by the benefit $b$ to the recipient is greater than the reproductive cost $c$ to the actor. This is also known as Hamilton's Rule:
\begin{equation} \label{hamiltonrule}
c<rb
\end{equation}
There is an ongoing debate about to what extent kin selection explains evolution of cooperation and altruism.
It has been suggested that kin selection to explain the cooperative behaviour of eusocial insects like the honey bee.
The most significant argument against kin selection is that cooperation can evolve with zero relatedness \cite{wilson2005kin}. This makes Hamilton's rule incomplete according to Wilson \cite{wilson2005kin}. Foster et al. \cite{foster2006kin} reject this claim. They argue that altruism without relatedness can not evolve. They refer us to Hamilton who claimed that relatedness can arise without recent common ancestry. 
Wilson also criticises kin selection on the grounds that environmental or ecological factors probably be more important than relatedness in determining social actions. On the other hand, Foster et al. \cite{foster2006kin} argue that kin selection does not ignore ecology. Hamilton’s rule shows
that environmental factors causing a high benefit: cost ratio will favour cooperation. \\\\\textbf{Reciprocity} suggests repeating interactions or individual recognition as key factors for explaining the evolution of cooperation. In \textit{direct reciprocity} there are a repeated encounters between the same two individuals. In every encounter, each player has a choice between cooperation and defection. If I cooperate now, you may cooperate later. Hence, it may pay off to cooperate.
This game-theoretic framework is known as the repeated Prisoner's Dilemma. 
%A well known strategy to play this game is called  'tit-for-tat'. This strategy always starts with a cooperation, then it does whatever the other player has done in the previous round: a cooperation for a cooperation, a defection for a defection. There a unlimited number of possible strategies to play this game. However, 
Direct reciprocity can only lead to the evolution of cooperation if the cost is smaller than $w$ the probability for another encounter between the same two individuals multiplied by the benefit. 
\begin{equation} \label{reciprocity}
c<bw
\end{equation}
Direct reciprocity assumes that both players are in a position to cooperate. Direct reciprocity can not explain cooperation in asymmetric interactions. In humans, such interactions happen often, for example humans often donate money. 
\textit{Indirect reciprocity} has been suggested to explain this behavior. 
Nowak \cite{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money. The money that "fuels the engines" of indirect reciprocity is reputation. 
\\However, Reciprocity assume repeating interactions and therefore, has difficulty explaining evolution of cooperation if the no repeating interactions occurs. 
\\\\\textbf{Group Selection} theory posits that cooperation is favoured because of the advantage to the whole group, if selection acts at the group level in addition to the individual level. A common model for group selection work as is: the population is divided into groups. In each groups there are cooperators, which help to other group members and defectors which do not help. 
Individuals reproduce proportional to their fitness. Offspring are added to the same group.
If a group reaches a certain size it can split to two groups. A group that grow faster will split more often. Groups of cooperators are growing faster than group of defectors.
Therefore, cooperation can evolve in this model when the ratio between benefit b and cost c is more than one plus the ratio between the maximum group size n and the number of groups m:
\begin{equation} \label{groupselection}
\frac{b}{c}>1+\frac{n}{m}
\end{equation}
The group selection was criticized by biologists advocate gene-centered view of evolution. Group selection has been criticized due to the fact that the trait like cooperation evolves in the total population. According to natural selection, if cooperation took over the population it must have better fitness. However, in group selection the fitness of cooperator in the individual level is lower. The fact that a trait with a lower fitness took over the population is a contradiction. Eldar et al. \cite{eldakar2011eight} reject this argument. They believe that this argument is a tautology and does not qualify as an argument against group selection. The distinction between individual and group selection requires a comparison of fitness differentials within and among groups in a multi group population. When a trait is evolve by group selection, despite the fact that it has lower fitness within the group, it has a better fit, all thing considered. 
\\\\All three theories mentioned above assume that cooperation is genetically determined. This raise the question, is it possible that cooperation is determined by environmental or social influences. Recent work by Lewin-Epstein at el.\cite{lewin2017microbes} may answer this question. 
Lewin-Epstein at el. \cite{lewin2017microbes} have proposed a different model that can explain the evolution of  cooperative behavior. They have hypothesized that microbes that manipulate their hosts to act altruistically could be favoured by selection, and may play a role in the widespread occurrence of cooperative behavior. Indeed, it has been shown that microbes can mediate behavioural changes in their hosts\cite{poulin2010parasite}\cite{dobson1988population}. Therefore, natural selection on microbes may favour manipulation of the host so that it cooperates with others. Microbes can be transmitted \textbf{horizontally} from one host to another during host interactions. Following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donating host, even when the two hosts are unrelated \cite{lewin2017microbes}. Microbes can also transfer vertically, from parent to
offspring. As a result, a microbe that induces its host to help another host, increases the other host survival or reproduction, thus increasing the vertical transmission (v) of the microbes of the receiving individual. Kin selection among microbes could therefore favour microbes that induce cooperative behaviour in their hosts, thereby increasing the transmission of their microbial kin.
\\While the hypothesis that microbes could manipulate their hosts to act altruistically is mathematically feasible \cite{lewin2017microbes}, there are still no empirical evidence of whether microbes indeed mediate altruistic behaviour of their hosts.

\subsection*{A Theory of Cultural Evolution of Cooperation}
From Lewin-Epstein at el. \cite{lewin2017microbes} we learn that \textbf{non-vertical} transmission could explain the evolution of cooperative behavior. 
Non-vertical transmission could be either a horizontal or oblique. Horizontal transmission is a transmission between individuals from the same generation. Oblique transmission is a transmission from an adult to a child. 
Evolution under either of these transmission models is expected to be more rapid than under pure vertical transmission \cite{ram2018evolution}.   
Here we suggest a model in which behavior changes are caused by cultural and social transmissions. In our model the social transmission that affects individual behavior can be learned during social interactions. For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behavior and will cooperate in the future. Surprisingly, much of the analysis made by Lewin-Epstein at el. \cite{lewin2017microbes} can be applied to cultural transmission, because learning can be modeled as infectious agent that transmits the cooperative behavior \cite{cavalli1981cultural}.

We \textbf{hypothesize} that non-vertical transmission can explain the evolution of cooperation. To test this hypothesis we are going to use cultural evolution models that include non-vertical transmission mechanism. We will use both mathematical analysis to investigate the models, and run simulations for more complex scenarios.

\section*{Research Proposal}
The research schedule can be found in appendix B. 
\subsection*{Aim 1} Our first aim is to determine to what extent non-vertical transmission can explain the evolution of cooperation in fully mixed population with prisoner's dilemma payoff.
We will develop a cultural evolution model and determine under which conditions cooperative behavior could prosper. The model assumes fully mixed population and individuals that interact in pairs with prisoner's dilemma payoff. The payoff matrix is shown in figure \ref{fig:payoff}. 
\\In our model We consider a population of asexual individuals. We assume that cooperative behavior is a dichotomous cultural trait with phenotypes A and B.  Individuals of type A will always act altruistically and individuals of type B will not cooperate. An individual who cooperates will pay a cost $0<c<1$ and the recipient gains a benefit $b$ where $b>c$.
After each interaction, each individual will try to learn from its interaction partner with probability $\alpha$, and with probability $1-\alpha$ it will try to learn from random individual within the population as shown in table \ref{fig:payoff}. 
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.5]{payoff.pdf}
  \caption{Payoff Matrix}
  \label{fig:payoff}
\end{figure}

@@

The question we are interested in is under what conditions the cooperative behavior represented by phenotype A will not become extinct. In order to do that we will investigate when $p' > p$.
We can make a simplify assumption that vertical transmission is perfect, $v=1$ and then we will be able to solve the inequation more easily. Under this assumption equations \eqref{aim1model0},\eqref{aim1model} become

\begin{equation} 
\begin{split}\label{modeleq}
p' =& \frac{1}{\overline{\omega}} \{ p^2(1+b-c)[1-(1-\alpha)T_Bq] + pq(1-c)[1-(1-\alpha)T_Bq-\alpha T_B)]\\
&+ pq(1+b)[\alpha T_A+(1-\alpha)T_Ap)] + q^2(1-\alpha)T_Ap\}.
\end{split}
\end{equation}
However, we are also interested when this assumption does not apply, meaning that $v<1$. In this, We will to run numerical simulation in order to better understand under what conditions cooperative behavior will take over the population. 
\\\textbf{\underline{Preliminary Results}}
We have preliminary result only when $v=1$.
\\We get that $p'>p$ when (see appendix A):
\begin{equation} 
\begin{split} \label{result0}
 c(1-T_B) < & \,  bqT_B(1-\alpha) - bqT_A(1-\alpha) + (T_A-T_B) + b(T_A - T_B) + \alpha bT_B
\end{split}
\end{equation}
We want to investigate few special cases:
\\\underline{Special case 1 - $T_A = T_B = T$:} then, eq. \eqref{result0} becomes:
\begin{equation}
\begin{split} \label{result}
 \frac{1-T}{\alpha T}< \frac{b}{c}
\end{split}
\end{equation}
Therefore, cooperative behavior will take over the population when eq. \eqref{result} is satisfied.  
\\\underline{Special case 2 - $\alpha =1$:} in this case, horizontal transmission can only occur as a result of interaction.
\\Eq. \eqref{result0} becomes:
\begin{equation} 
\begin{split} \label{result3}
c(1-T_B)  < & \, T_A -T_B +b(T_A-T_B)
\end{split}
\end{equation}
Therefore, cooperative behavior will take over the population when eq. \eqref{result3} is satisfied. 
This result is in accordance with the result presented by Lewin-Epstein at el. \cite{Ohad}. 
\\\underline{Special case 3 - $\alpha = 0$:} in this case horizontal transmission can not occur as a result of interaction.  
Then, eq. \eqref{result0} becomes:
\begin{equation} 
\begin{split} \label{result4}
0 < & \,  - bq(1-T_B)- bT_B-c(1-T_B)-T_B
\end {split}
\end{equation}
Which is always false because all of the elements are negative. Therefore, cooperation will eventually disappear from population.
\\Those are the results we have so far. However, there is a still work need to be done. \\
We will analyze the equilibrium points in this model. We know that $p=1$ is an equilibrium point because if the all individuals in the population are cooperators then in next generation all individual will be cooperator as well. Same for $p=0$. We will check if there are any more equilibrium points. For each equilibrium point we will determine whether it is stable equilibrium or not. 
\\So far, we assumed that $v=1$. We believe it will be interesting to test the effect of oblique transmission ($v\neq 1$) since oblique transmission is common in cultural evolution models. Therefore, we are planning to simulations to investigate the case when $v\neq 1$.

@@

\newpage
\section*{Appendix B - Research Schedule}
\begin{figure}[h!]
  \centering
  \includegraphics[scale=1]{schdule2.pdf}
\end{figure}

>>>>

\title{Can Cultural Transmission Explain The Evolution of Cooperative Behaviour}
\author{Dor Cohen \\ cohensdor@gmail.com \and Yoav Ram \\ yoav@yoavram.com}
\date{School of Computer Science, IDC Herzliya, Israel\\ \today}

@@

\section*{Introduction}
Cooperative behaviour can harm the individual's fitness and increase the fitness of its competitor~\cite{axelrod1981evolution}.
Yet, cooperative behaviour occurs in many non-human animals~\cite{dugatkin1997cooperation}, for example rats~\cite{rice1962altruism} and birds~\cite{krams2008experimental}.
Therefore, the evolution of cooperative behaviour is an important open question in evolutionary biology.
\\
Cultural evolution is an evolutionary theory of social change.
Culture has significant impact on the behaviour of humans~\cite{ihara2004cultural,jeong2018bronze} as well as non-human animals~\cite{bonner2018evolution}.
Under the view of cultural evolution, an individual can acquire its behaviour from another individual in its social group through learning or other modes of cultural transmission \cite{richerson2008not}.
Here we attempt to determine to what extent cultural transmission can explain the evolution of cooperative behaviour.

\subsection*{Theories for Evolution of Cooperation}
Three major theories have been proposed to explain the evolution of cooperative behaviour.

\textbf{Kin selection}, proposing that natural selection can favour cooperative behaviour between kin. The importance of relatedness to the evolution of cooperation and altruism was shown by Hamilton~\cite{hamilton1964genetical}. According to Hamilton, kin selection causes allele to increase in frequency when the genetic relatedness $r$ of a recipient to an actor multiplied by the benefit $b$ to the recipient is greater than the reproductive cost $c$ to the actor. This is also known as Hamilton's Rule:
\begin{equation} \label{hamiltonrule}
c<rb
\end{equation}
There is an ongoing debate about to what extent kin selection explains evolution of cooperation and altruism.
It has been suggested that kin selection to explain the cooperative behaviour of eusocial insects like the honey bee.
The most significant argument against kin selection is that cooperation can evolve with zero relatedness~\cite{wilson2005kin}. This makes Hamilton's rule incomplete according to Wilson~\cite{wilson2005kin}. Foster et~al.~\cite{foster2006kin} reject this claim. They argue that altruism without relatedness can not evolve. They refer us to Hamilton who claimed that relatedness can arise without recent common ancestry. 
Wilson also criticises kin selection on the grounds that environmental or ecological factors probably be more important than relatedness in determining social actions. On the other hand, Foster et~al.~\cite{foster2006kin} argue that kin selection does not ignore ecology. Hamilton’s rule shows
that environmental factors causing a high benefit-to-cost ratio will favour cooperation.

\textbf{Reciprocity} suggests repeating interactions or individual recognition as key factors for explaining the evolution of cooperation. In \textit{direct reciprocity} there are a repeated encounters between the same two individuals. In every encounter, each player has a choice between cooperation and defection. If I cooperate now, you may cooperate later. Hence, it may pay off to cooperate.
This game-theoretic framework is known as the repeated Prisoner's Dilemma. 
%A well known strategy to play this game is called  'tit-for-tat'. This strategy always starts with a cooperation, then it does whatever the other player has done in the previous round: a cooperation for a cooperation, a defection for a defection. There a unlimited number of possible strategies to play this game. However, 
Direct reciprocity can only lead to the evolution of cooperation if the cost is smaller than $w$ the probability for another encounter between the same two individuals multiplied by the benefit. 
\begin{equation} \label{reciprocity}
c<bw
\end{equation}
Direct reciprocity assumes that both players are in a position to cooperate. Direct reciprocity can not explain cooperation in asymmetric interactions. In humans, such interactions happen often, for example humans often donate money.

\textbf{Indirect reciprocity} has been suggested to explain this behaviour. 
Nowak~\cite{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money. The money that "fuels the engines" of indirect reciprocity is reputation. 
\\However, Reciprocity assume repeating interactions and therefore, has difficulty explaining evolution of cooperation if the no repeating interactions occurs.

\textbf{Group Selection} theory posits that cooperation is favoured because of the advantage to the whole group, if selection acts at the group level in addition to the individual level. A common model for group selection work as is: the population is divided into groups. In each groups there are cooperators, which help to other group members and defectors which do not help. 
Individuals reproduce proportional to their fitness. Offspring are added to the same group.
If a group reaches a certain size it can split to two groups. A group that grow faster will split more often. Groups of cooperators are growing faster than group of defectors.
Therefore, cooperation can evolve in this model when the ratio between benefit b and cost c is more than one plus the ratio between the maximum group size n and the number of groups m:
\begin{equation} \label{groupselection}
\frac{b}{c}>1+\frac{n}{m}
\end{equation}
The group selection was criticized by biologists advocate gene-centered view of evolution. Group selection has been criticized due to the fact that the trait like cooperation evolves in the total population. According to natural selection, if cooperation took over the population it must have better fitness. However, in group selection the fitness of cooperator in the individual level is lower. The fact that a trait with a lower fitness took over the population is a contradiction. Eldar et al.~\cite{eldakar2011eight} reject this argument. They believe that this argument is a tautology and does not qualify as an argument against group selection. The distinction between individual and group selection requires a comparison of fitness differentials within and among groups in a multi group population. When a trait is evolve by group selection, despite the fact that it has lower fitness within the group, it has a better fit, all thing considered.

All the above theories assume that cooperation is genetically determined. This raises the question, is it possible that cooperation is determined by non-genetic factors?
Recent work by Lewin-Epstein at el.~\cite{lewin2017microbes} sheds some light on this question. 
Lewin-Epstein at el.~\cite{lewin2017microbes} have hypothesised that microbes that manipulate their hosts to act altruistically can be favoured by selection, and may play a role in the widespread occurrence of cooperative behaviour. Indeed, it has been shown that microbes can mediate behavioural changes in their hosts~\cite{poulin2010parasite,dobson1988population}. Therefore, natural selection on microbes may favour manipulation of the host so that it cooperates with others. Microbes can be transmitted \emph{horizontally} from one host to another during host interactions. Following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donor host, even when the two hosts are (genetically) unrelated~\cite{lewin2017microbes}. Microbes can also transfer vertically, from parent to offspring (yr: cite 10.1126/science.aat7164). As a result, a microbe that induces its host to cooperate with another host and thereby increases the other host fitness will  increase the vertical transmission of the microbes of the receiving individual. Kin selection among microbes could therefore favour microbes that induce cooperative behaviour in their hosts, thereby increasing the transmission of their microbial kin.
%\\While the hypothesis that microbes could manipulate their hosts to act altruistically is mathematically feasible~\cite{lewin2017microbes}, there are still no empirical evidence of whether microbes indeed mediate altruistic behaviour of their hosts.

\subsection*{Cultural Evolution of Cooperation}
Lewin-Epstein at el.~\cite{lewin2017microbes} have demonstrated that \emph{non-vertical} transmission can help to explain the evolution of cooperative behaviour. 
Non-vertical transmission could be either a horizontal or oblique. Horizontal transmission occurs between individuals from the same generation. Oblique transmission occurs from an adult to an offspring. 
Evolution under either of these transmission models is can be be more rapid than under pure vertical transmission \cite{ram2018evolution} (yr: not sure this is a good reference).

Here we suggest a model in which behavioural changes are mediated by cultural transmission that can occur during social interaction. For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behaviour and will cooperate in the future. Surprisingly, some of the analysis made by Lewin-Epstein at el.~\cite{lewin2017microbes} can be applied to cultural transmission, because cultural transmission is mathematically akin to transmission of infectious diseases~\cite{cavalli1981cultural}.

Here, we hypothesise that non-vertical cultural transmission can explain the evolution of cooperation. We are develop cultural evolution models that include both vertical and non-vertical transmission of cooperation and investigate these models using both mathematical analysis and simulations.

\section*{Models and Methods}

Our first aim is to determine to what extent non-vertical transmission can explain the evolution of cooperation in a fully mixed population where cooperation is modelled using the prisoner's dilemma (yr: add ref).

Consider a fully mixed asexual population where individuals interact in pairs with a prisoner's dilemma payoff~\ref{fig:payoff}.

Cooperative behaviour is a dichotomous cultural trait with phenotypes $A$ and $B$ for cooperation and defection, respectively. Cooperators pay a cost $0<c<1$ and their partner gains a benefit $b$, where we assume $b>c$.
After each interaction, each individual will try to learn from its interaction partner with probability $\alpha$, and with probability $1-\alpha$ it will try to learn from random individual within the population as shown in table \ref{fig:payoff}. 
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.5]{payoff.pdf}
  \caption{Payoff Matrix}
  \label{fig:payoff}
\end{figure}

@@

The question we are interested in is under what conditions the cooperative behaviour represented by phenotype A will not become extinct. In order to do that we will investigate when $p' > p$.
We can make a simplify assumption that vertical transmission is perfect, $v=1$ and then we will be able to solve the inequation more easily. Under this assumption equations \eqref{aim1model0},\eqref{aim1model} become

\begin{equation} 
\begin{split}\label{modeleq}
p' =& \frac{1}{\overline{\omega}} \{ p^2(1+b-c)[1-(1-\alpha)T_Bq] + pq(1-c)[1-(1-\alpha)T_Bq-\alpha T_B)]\\
&+ pq(1+b)[\alpha T_A+(1-\alpha)T_Ap)] + q^2(1-\alpha)T_Ap\}.
\end{split}
\end{equation}
However, we are also interested when this assumption does not apply, meaning that $v<1$. In this, We will to run numerical simulation in order to better understand under what conditions cooperative behaviour will take over the population. 
\\\textbf{\underline{Preliminary Results}}
We have preliminary result only when $v=1$.
\\We get that $p'>p$ when (see appendix A):
\begin{equation} 
\begin{split} \label{result0}
 c(1-T_B) < & \,  bqT_B(1-\alpha) - bqT_A(1-\alpha) + (T_A-T_B) + b(T_A - T_B) + \alpha bT_B
\end{split}
\end{equation}
We want to investigate few special cases:
\\\underline{Special case 1 - $T_A = T_B = T$:} then, eq. \eqref{result0} becomes:
\begin{equation}
\begin{split} \label{result}
 \frac{1-T}{\alpha T}< \frac{b}{c}
\end{split}
\end{equation}
Therefore, cooperative behaviour will take over the population when eq. \eqref{result} is satisfied.  
\\\underline{Special case 2 - $\alpha =1$:} in this case, horizontal transmission can only occur as a result of interaction.
\\Eq. \eqref{result0} becomes:
\begin{equation} 
\begin{split} \label{result3}
c(1-T_B)  < & \, T_A -T_B +b(T_A-T_B)
\end{split}
\end{equation}
Therefore, cooperative behaviour will take over the population when eq. \eqref{result3} is satisfied. 
This result is in accordance with the result presented by Lewin-Epstein at el. \cite{Ohad}. 
\\\underline{Special case 3 - $\alpha = 0$:} in this case horizontal transmission can not occur as a result of interaction.  
Then, eq. \eqref{result0} becomes:
\begin{equation} 
\begin{split} \label{result4}
0 < & \,  - bq(1-T_B)- bT_B-c(1-T_B)-T_B
\end {split}
\end{equation}
Which is always false because all of the elements are negative. Therefore, cooperation will eventually disappear from population.
\\Those are the results we have so far. However, there is a still work need to be done. \\
We will analyze the equilibrium points in this model. We know that $p=1$ is an equilibrium point because if the all individuals in the population are cooperators then in next generation all individual will be cooperator as well. Same for $p=0$. We will check if there are any more equilibrium points. For each equilibrium point we will determine whether it is stable equilibrium or not. 
\\So far, we assumed that $v=1$. We believe it will be interesting to test the effect of oblique transmission ($v\neq 1$) since oblique transmission is common in cultural evolution models. Therefore, we are planning to simulations to investigate the case when $v\neq 1$.

@@
